Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2024-10-23 02_paper/02_study/02_expertise_paper/paper_methods.Rmd
x paper

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

@@

# changing Type of School into character
# LI18:
# 1: Grundschule
# 2: Oberschule
# 3: Gymnasium
# 4: Förderschule/Sondershausen
# 5: Berufsbildende Schule
# -1: andere Schulform
demo.data$School_type <- factor(x = demo.data$School_type,
                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`). 
`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers. `r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

@@

# read in data and combine multiple excel sheets into a single table 
sri <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
  dplyr::select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns
  dplyr::filter(!`Disruption Factor` == -100,
           !`Confident Factor` == -100,
           !`Disruption Factor`== -99,
           !`Confident Factor` == -99)

############## Disruption Factor #########################

sri.disrup.table <- 
  sri %>%
  group_by(Group, Event) %>%
  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
  summarise("M" = round(mean(`Disruption Factor`), 
                        digits = 2),
            "SD" = round(sd(`Disruption Factor`),
                         digits = 2),
            "Min" = min(`Disruption Factor`),
            "Max" = max(`Disruption Factor`))

# format and insert table in manuscript
papaja::apa_table(
sri.disrup.table,
  caption = "Table Rating Scales Disruption Factor",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

############## Confident Factor #########################

sri.confi.table <- 
  sri %>%
  group_by(Group, Event) %>%
  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
  summarise("M" = round(mean(`Confident Factor`), 
                        digits = 2),
            "SD" = round(sd(`Confident Factor`),
                         digits = 2),
            "Min" = min(`Confident Factor`),
            "Max" = max(`Confident Factor`))

# format and insert table in manuscript
papaja::apa_table(
sri.confi.table,
  caption = "Table Rating Scales Confident Factor",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

>>>>

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201,
         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

@@

# changing Type of School into character
# LI18:
# 1: Grundschule
# 2: Oberschule
# 3: Gymnasium
# 4: Förderschule
# 5: Berufsbildende Schule
# -1: andere Schulform
demo.data$School_type <- factor(x = demo.data$School_type,
                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`). 
`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Vocational School") %>% pull("Percent_schooltype") %>% unique()`% were vocational school teachers. `r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

@@

# # read in data and combine multiple excel sheets into a single table 
# sri <- 
#   excel_sheets("data/Coding_SRI.xlsx") %>% 
#   map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
#   dplyr::select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns
#   dplyr::filter(!`Disruption Factor` == -100,
#            !`Confident Factor` == -100,
#            !`Disruption Factor`== -99,
#            !`Confident Factor` == -99)
# 
# ############## Disruption Factor #########################
# 
# sri.disrup.table <- 
#   sri %>%
#   group_by(Group, Event) %>%
#   mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
#   summarise("M" = round(mean(`Disruption Factor`), 
#                         digits = 2),
#             "SD" = round(sd(`Disruption Factor`),
#                          digits = 2),
#             "Min" = min(`Disruption Factor`),
#             "Max" = max(`Disruption Factor`))
# 
# # format and insert table in manuscript
# papaja::apa_table(
# sri.disrup.table,
#   caption = "Table Rating Scales Disruption Factor",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
# )
# 
# ############## Confident Factor #########################
# 
# sri.confi.table <- 
#   sri %>%
#   group_by(Group, Event) %>%
#   mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
#   summarise("M" = round(mean(`Confident Factor`), 
#                         digits = 2),
#             "SD" = round(sd(`Confident Factor`),
#                          digits = 2),
#             "Min" = min(`Confident Factor`),
#             "Max" = max(`Confident Factor`))
# 
# # format and insert table in manuscript
# papaja::apa_table(
# sri.confi.table,
#   caption = "Table Rating Scales Confident Factor",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
# )
